The imprint of global magma oceans on exoplanet demographics

### 2023-03-07 src/tex/ms.tex
minor edits

\subsubsection{Stellar sample from Gaia DR3}
%Different sample sizes are realized by varying the maximum distance of stars to the solar system $d_\mathrm{max}$.
%\todo[inline]{KEVIN: describe stellar population}
\todo[inline]{KEVIN: update reference to my paper once accepted}
The original \texttt{Bioverse} stellar catalog was generated randomly from the \citet{Chabrier2003} stellar mass function. Exquisite parallax and photometric data from the \textit{Gaia} mission made it possible for Hardegree-Ullman et al. (submitted) to generate a homogeneous and complete stellar catalog out to about 100~pc, which became the new standard stellar catalog for \texttt{Bioverse}. Here, we briefly describe how stellar parameters $T_{\mathrm{eff}}$, $L_{\star}$, $R_{\star}$, and $M_{\star}$ were derived for \texttt{Bioverse}, but for a full description, please refer to Hardegree-Ullman et al. (submitted).

Hardegree-Ullman et al. (submitted) used the Gaia Catalogue of Nearby Stars \citep[hereafter GCNS,][]{Smart2021} as the basis for deriving stellar parameters for the \texttt{Bioverse} catalog. The GCNS identified stars out to 120~pc, and includes \textit{Gaia} DR3 parallaxes and photometry in $G$, $G_{BP}$, and $G_{RP}$ bands \citep{GaiaCollaboration2021} and $K_S$ band photometry from 2MASS \citep{Cutri2003}, all of which were used in stellar classification. From this information, colors and absolute magnitudes were computed, and initial color-magnitude cuts were made to remove non-main sequence stars. Effective temperatures were computed primarily from color-temperature relations derived using the main sequence stellar parameters table from \citet{Pecaut2013}. Next, luminosities were computed from absolute $G$-band magnitudes and a derived bolometric correction. Stellar radii were then computed with the effective temperatures and lumonisities using the Stefan-Boltzmann law, or using absolute $K_S$-band magnitudes and an empirical radius-luminosity relation from \citet{Mann2015} for targets within the absolute magnitude range of M dwarfs. Finally, masses were derived from either the mass-luminosity relation of \citet{Torres2010} for stars with $M_{\star}\gtrsim0.7\,M_{\odot}$, and that of \citet{Mann2019} for targets within the absolute magnitude range of M dwarfs. The derived stellar parameters from Hardegree-Ullman et al. (submitted) were compared to measured stellar parameters for all known exoplanet hosts from the literature and were found to be consistent within 1\%, 3\%, and 5.5\% for $T_{\mathrm{eff}}$, $R_{\star}$, and $M_{\star}$, respectively, which are all below the typical measurement uncertainties of 3.3\%, 6.8\%, and 7.9\%, respectively.

>>>>

\subsubsection{Stellar sample from Gaia DR3}
%Different sample sizes are realized by varying the maximum distance of stars to the solar system $d_\mathrm{max}$.
%\todo[inline]{KEVIN: describe stellar population}
\todo[inline]{KEVIN: update reference to my paper once accepted}
The original \texttt{Bioverse} stellar catalog was generated randomly from the \citet{Chabrier2003} stellar mass function. Exquisite parallax and photometric data from the \textit{Gaia} mission made it possible to generate a homogeneous and complete stellar catalog out to about 100~pc, which became the new standard stellar catalog for \texttt{Bioverse}~(Hardegree-Ullman et al., submitted). Here, we briefly describe how stellar parameters $T_{\mathrm{eff}}$, $L_{\star}$, $R_{\star}$, and $M_{\star}$ were derived.

Hardegree-Ullman et al. (submitted) used the Gaia Catalogue of Nearby Stars \citep[hereafter GCNS,][]{Smart2021} as the basis for deriving stellar parameters for the \texttt{Bioverse} catalog. The GCNS identified stars out to 120~pc, and includes \textit{Gaia} DR3 parallaxes and photometry in $G$, $G_{BP}$, and $G_{RP}$ bands \citep{GaiaCollaboration2021} and $K_S$ band photometry from 2MASS \citep{Cutri2003}, all of which were used in stellar classification. From this information, colors and absolute magnitudes were computed, and initial color-magnitude cuts were made to remove non-main sequence stars. Effective temperatures were computed primarily from color-temperature relations derived using the main sequence stellar parameters table from \citet{Pecaut2013}. Next, luminosities were computed from absolute $G$-band magnitudes and a derived bolometric correction. Stellar radii were then computed with the effective temperatures and lumonisities using the Stefan-Boltzmann law, or using absolute $K_S$-band magnitudes and an empirical radius-luminosity relation from \citet{Mann2015} for targets within the absolute magnitude range of M dwarfs.
Finally, masses were derived from the mass-luminosity relation of \citet{Torres2010} for stars with $M_{\star}\gtrsim0.7\M_{\odot}$, and from that of \citet{Mann2019} for targets within the absolute magnitude range of M dwarfs. The derived stellar parameters from Hardegree-Ullman et al. (submitted) were compared to measured stellar parameters for all known exoplanet hosts from the literature and were found to be consistent within 1\%, 3\%, and 5.5\% for $T_{\mathrm{eff}}$, $R_{\star}$, and $M_{\star}$, respectively, which are all below the typical measurement uncertainties of 3.3\%, 6.8\%, and 7.9\%, respectively.
